Different forms of uncertainty differently affect the evolution of social learning

### 2022-07-18 ms.tex
nearly done with full revision

\textbf{Effective lifespan.}
Learning can be viewed as a process by which an individual reduces or otherwise manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}. It is an iterative process by which one repeatedly acquires information, forms representations and predictions, and tests and refines those representations and predictions. It therefore stands to reason that the more opportunities one has for learning, the more one can in principle reduce one's uncertainty, assuming the environment has not changed in the meantime. Similarly, a reduction in the number of opportunities to learn will increase the uncertainty about whether one has accurately learned about the available behavioral options and their associated payoffs. We refer to the number of learning opportunities as an individual's effective lifespan to imply that it is the number of opportunities to learn throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.

Empirically, the number of learning opportunities can be manipulated in the lab, but will also correspond with an individual's age the real world. In multi-round studies of information use in novel tasks, US participants' use of social information declined precipitously across rounds ~\cite{McElreath2005}, suggesting they were more likely to use social information when they were most uncertain about the task early on. In a more naturalistic context, Aplin et al. (2017) \nocite{Aplin2017} found that younger great tits more readily used social information compared with older individuals, possibly because they had accrued less information via individual learning, and also possibly because younger individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options. \ps{I got rid of the Leris and Reader reference because it didn't seem relevant to age-based uncertainty. They just showed that young guppies exposed to reliable models were more likely to use social information later. I also added some human studies, which seems important.} Cross-cultural studies on humans have shown the importance of childhood as a phase of heavy social learning ~\cite{Reyes2016}. Young children are more likely to acquire their beliefs and simple skills from their parents than are older children or adults, which is at least partly due to the differential knowledge accrual between young children and the older adults to whom they direct the most trust and attention \cite{kline2013teaching}.
%The age of individuals was found to have an effect on social learning in both \emph{parus major}~\cite{Aplin2017} and \emph{poecilia reticulata} (guppies)~\cite{Leris2016}. \ps{What effect? I'm not sure }
%\mt{Need better connection between lifespan and age, or better references to support use of lifespan}.
Individuals with shorter effective lifespans will end their lives with more uncertainty about which behaviors are optimal, and thereby transmit some of that uncertainty to anyone who learns from them. The effective lifespan for learning varies across tasks, individuals, and species, yet most models assume one learning opportunity per generation ~\cite{Feldman1996,Henrich1998, perreault2012bayesian}. Some models do allow several cultural generations within 1 genetic generation ~\cite{Enquist2007}, but little formal theory explicitly examines the role of uncertainty based on number of learning opportunities into our understanding of the evolution of social learning.

@@

\begin{comment}

\cm{I think a lot of this may be too much detail. I'm still editing and focusing the above on the main forms of uncertainty we are modeling and reviewing the relevant literature as we go. Yes we've made choices about things like horizontal vs vertical, but i think we can just justify that when we introduce the model }
ps{I agree with Cristina here. I think we should use this section to justify our way of modeling individual and social learning, which is different from previous models. We don't need to provide a detailed review, just why it's worth doing it as we've done it. In particular, we should set up (1) social learning as an initial scaffold for future social learning, and (2) softmax individual learning which involves some greediness with occasional trial and error.}

To add to confusion about how to integrate diverse models of social learning
evolution, different models select different social learning components in
seemingly \emph{ad hoc} ways 
\begin{itemize}
  \item 
    Vertical, oblique, horizontal transmission
  \item
    Conformity, payoff-biased, frequency-dependent, etc. A note about how
    ``conformity'' is often not distinguished from other forms of social learning
  \item
    Review human studies
  \item
    Review non-human studies~\cite{Leris2016,Aplin2017,Avargues-Weber2018,Baracchi2018}
  \item
    One sentence on how dual-inheritance theory enables us to gloss over whether
    social learning is genetically or culturally evolved.
  \item
    More things from which we selected the operation of our model
\end{itemize}

\end{comment}

@@

In \emph{evolutionary} agent-based models like ours, agent life cycles are
programmed to cause agents to reproduce and die off, where reproducers pass on
heritable traits to their offspring. This sets up an inter-generational structure
that we also use as a scaffold for social learning: we assume social learning occurs
\emph{obliquely}\mt{is ``oblique learning'' understood to include parents by default
or do we need to say ``or vertically''?}, meaning learning happens when a new
generation of agents each select a teacher from the previous generation, possibly
including their parents.  Natural selection occurs in the model when agents with higher
payoffs preferentially reproduce. This is a model of cultural evolution, so
``reproduction'' means teaching the meta-cognitive strategy of whether one should learn
socially at all; ``death'', in this interpretation, means
loss of the potential to socially influence others. 
Evolutionary agent-based models are powerful, but their components need to be
carefully specified and justified in relation to empirical facts.

@@

% \begin{itemize}
%   \item
%     Softmax-guided behavior selection
%   \item
%     Oblique learning, not horizontal; no intragenerational change in optimal
%     behavior, only intergenerational
%   \item 
%     Payoff-biased teacher selection, not aggregation over everyone or large group,
%     as in conformist transmission
%   \item
%     Not spatial in any way. Agents need only to choose among potential behaviors
%     and the behavior is instantly performed, as a real human can when pointing
%     and clicking on a computer screen. This approximation could also hold when
%     all behavioral options require an identical amount of time/money/resources
%     to enable the agent to actually do the behavior (drive to work, walk to a
%     watering hole, fly to a flower to gather pollen, etc.). Since teacher and
%     behavior selection and reproduction are biased by relative payoffs there
%     is no effect on model dynamics if cost of access is the same for each behavior.
% \end{itemize}

@@

\begin{itemize}
  \item 
    A number of parameters specify the structure of the environment in which
    agents sovle problems and adapt by adjusting their social learning through
    evolution. \mt{Introduce all parameters; do not give values, but ref
    (Table~\ref{tab:uncertaintyParameters})}
  \item
    \mt{Bandits and payoffs in more detail}
\end{itemize}

\vspace{2em}
\begin{table}[h]
\caption{Uncertainty parameters.  Bold indicates default value tested} %\emph{default value tested}.}
    \label{tab:uncertaintyParameters}
    \centering %\hspace{-3em}
    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule

@@

All agents perform individual, trial-and-error learning over their lifespan.
This learning is guided based on the softmax search algorithm which drives
agents to explore all behavioral options in the selection set when 
the agent is more uncertain which is optimal, and to exploit the most profitable
behaviors more frequently when the agent is more certain which are most beneficial. 
To do softmax searching, agents track payoffs acquired from each behavior.
(introduce agent attributes)
When agents are initialized at the start of the model, all agents are initialized
with all $\pi_{ib} = 0$. At the start of generations other than the first, 
$\pi_i$ will be initialized with all $\pi_{ib} = 0$ for asocial learners ($s_i = 0$)
or with a teacher's $\pi_{ib}$. 
Agents are thus endowed with dynamic attributes to track payoffs and calculate the
softmax weights, and with an instruction of whether child agents learn socially
or not. Details of how these attributes are updated over time is explained below
with the rest of the model dynamics.

\begin{table}[h]
  \caption{Agent-level variables. The first four ($\protect s_i$, $\protect
    \bar\pi_{ib}$, $\protect c_{ib}$,
  and $\protect \pi_i$) are dynamic with an implicit time dependence. The softmax
greediness $\protect \beta$ and number of prospective teachers for social learners,
$\protect N_T$, are constant throughout each simulation.}
    \label{tab:modelParameters}
    \centering %\hspace{-3em}
    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule

@@

\paragraph{Initialization}
At generation start, one of the behaviors is set to 
yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
expected payoffs $\pilow$. At each time step, agents perform behavior $b$ 
with softmax-weighted probability
\begin{equation}
  \Pr(\text{Agent $i$ performs behavior $b$}) = 
    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}},
\end{equation}
\noindent
where $\beta$ is a parameter that adjusts how frequently agents perform 
behaviors with high expected payoffs (larger $\beta$) versus how frequently
agents explore alternative behaviors (smaller $\beta$)~\cite{McElreath2005}. 
Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
bandit paid off. Behavior payoffs are represented as a draw from a 
Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from
behavior $b$.  For concreteness we denote this probabilistic payoff
$\bandit$. On performing behavior $b$, agent $i$ updates the
corresponding \emph{behavior count} by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
the expected payoffs calculated for that behavior are updated with
exponentially-weighted averaging
\begin{equation}
  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}}.
\end{equation}
\noindent
This procedure continues for $L$ time steps within each generation
(Figure~\ref{fig:schematic}B).

\paragraph{Intragenerational dynamics}
To guide behavior selection, agent $i$ counts how many times it
performed each behavior $b$, denoted $c_{ib}$. Agents use this count to 
update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
$\ledger$ is initialized to 0 for all $b$ at model start for
all agents (Figure~\ref{fig:schematic}A), and at 
generation start for asocial learners. Social
learning agents' $\ledger$ is initialized as that of its teacher, who is selected
through performance-biased oblique learning; $c_ib$ is set to 1 for all social
learners $i$ and behaviors $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
accumulated payoffs from performing several behaviors over their lifetime of $L$
time steps is denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write
$s_i = 1$, otherwise the agent is an asocial learner and $s_i = 0$.

\paragraph{Intergenerational dynamics}
In between generations agents first reproduce via asexual haploid reproduction; 
then new child agents learn from the
previous generation if they are social learners; and finally all agents from the
previous generation then die off (Figure~\ref{fig:schematic}C). 
$N$ reproducers are selected with replacement over $N$ independent draws, 
biased by performance:
\begin{equation}
  \Pr(\text{Agent $i$ is chosen to reproduce in one draw}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
\end{equation}
\noindent
A child inherits its parent's social learning trait $s_i$ without mutation.
A social learner child with $s_i = 1$ learns from a teacher from its parent's
generation, including possibly their parent (oblique learning). 
A child selects its teacher by first selecting $N_T$ prospective
teachers from the population completely at random, then selecting the one with
highest net payoffs $\pi_i$ as their teacher, with ties broken randomly ($N_T =
5$ in the main text; \mt{Other values will be tested in the supplement}). While it
is somewhat arbitrary to first subset $N_T$, this is a conservative choice that
represnts the fact that access to the entire population is not generally guaranteed.
Social learners adopt their chosen teacher's ledger of expected payoffs $\ledger$,
and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.  Asocial
learners ($s_i = 0$) are initialized with all $c_{ib} = 0$ and $\ledger = 0$ 
(Figure~\ref{fig:schematic}C). The
newly initialized population then begins behavior selection and payoff accumulation
for another $L$ time steps.

\paragraph{Stopping conditions} The evolutionary process continues until $\sum_i s_i
= 1$ or $\sum_i s_i = 0$.

\mt{I believe all trials will eventually end like this, so
in the next set of model runs I will not allow early termination before one of these
conditions are met}.

\subsection{Computational analyses}

@@

To analyze the effect of the four principal uncertainty factors, we systematically
varied their values and observed three key outcome variables aggregated across 1000
trial simulations, and across all agents when appropriate. We varied $u \in \{0.0,
0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L
\in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.  We observed
three outcome measures: (1) $\meansl$, the average value of $s_i$ over all agents
and trials; (2) $\meanpi / L$, the average net payoffs at simulation end across
agents and trials, normalized by lifespan; and (3) $\meanT / L$, 
or the mean number of time steps to fixation normalized by
lifespan\footnote{Equivalent to the mean number of generations to fixation}
(fixation means $\sum_i s_i = 0 \text{ or } 1$). \mt{Make sure to qualitatively
introduce these and their evolutionary importance in the intro.}
We analyze outcomes by plotting $\meansl$ on the y-axis and environmental
variation is on x-axis since we theoretically expect that $\meansl$ will 
decrease monotonically from 1 to 0 as $u$ increases. We expected and observed
that the other three uncertainty factors shift the value of $u$ at which 
$\meansl$ starts to decrease, and how rapidly $\meansl$ decreases. Note that the
hypothesis-testing concept of significance is meaningless here because we could
make any small outcome difference ``significant'' by running more simulation trials.
We instead study the patterns of outcome 
variables over systematically varied uncertainty factor values.

@@

@@

To understand how different forms of uncertainty interact to affect the evolution
of social learning, we measured simulated social learning prevalence across a 
suite of simulations over uncertainty parameters. We analyze simulation outcomes
by plotting the mean observed social learning frequency, $\meansl$ across all agents 
and 1000 simulation trials for each uncertainty parameter setting. We do not calculate
significance measures since these can be inflated by simply adding more trials.
Instead, we visualize and inspect plots with $\meansl$ on the y-axis and
environmental variability, $u$ on the x-axis. This is convenient because we are
most certain about how $\meansl$ depends on $u$: we expect $\meansl$ to decrease
as $u$ increases since environmental variability is well understood to cause
socially-transmitted information to become outdated. When the other forms of
uncertainty are varied, this causes changes to when and how quickly social learning
is suppressed as $u$ increases. To inspect these changes, we show nine plots
of $\meansl$ over $u$ in a 3x3 plot array (Figure~\ref{fig:mainResults}). 
Plot array columns correspond to different selection set sizes, $B$; rows
correspond to different non-optimal payoff values, $\pilow$ (recall optimal
payoff $\pihigh=0.9$ for all analyses); plot line and marker colors correspond
to different effective lifespan, $L$, values. 
We support our conclusions regarding the evolution of
social learning by analyzing the time to model 
fixation and by comparing the average net payoffs in our simulations to the
expected payoffs for individuals in both populations of all social learners
and in populations of all individual learners. We thus use our analysis 
to understand changes to how $\meansl$ changes over $u$ for different uncertainty parameter settings.

Several patterns emerged in changes to the shape of social learning suppression over
environmental variability, $u$, across different uncertainty contexts defined by the
payoff ambiguity, selection set size, and effective lifespan
(Figure~\ref{fig:mainResults}). When payoff ambiguity and selection set size were
both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when $u$ is small
since individual learning is relatively efficient in this case
(Figure~\ref{fig:mainResults}, upper left). As $\pilow$ increased the suppression of
$\meansl$ flattened over $u$, which was more pronounced for smaller $L$ (rows of
Figure~\ref{fig:mainResults}).  When $L$ is smaller, agents have fewer opportunities
to learn through trial and error, and so it is more difficult for them to discern
which strategy, social or asocial, is optimal. Increased selection set size led to
both a shift in the critical value of $u$ when $\meansl$ begins to decrease, and
flattened social learning suppression. This is because possibly misleading 
social information is less consequential due
to (1) larger $B$ is a more difficult problem for trial-and-error learning, and
(2) a misidentified optimal behavior is weighted less relative to smaller
$B$, meaning agents are more likely to explore behaviors identified as non-optimal
when $B$ is larger (columns of Figure~\ref{fig:mainResults}).  \mt{Support this by calculating the difference between weights when B=2 and B=10 and a social learner learns outdated information}
Increased $B$ led to more pronounced flattening of social learning suppression when
$L$ was small, apparently again because of the limited data available to evolution,
making individual outcomes more path dependent.

>>>>

\textbf{Effective lifespan.}
\mt{Restructure: lead with ``It stands to reason'' sentence or similar that gets
to the point of this par more quickly, that lifespan affects uncertainty.}
Learning can be viewed as a process by which an individual reduces or otherwise manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}. It is an iterative process by which one repeatedly acquires information, forms representations and predictions, and tests and refines those representations and predictions. It therefore stands to reason that the more opportunities one has for learning, the more one can in principle reduce one's uncertainty, assuming the environment has not changed in the meantime. Similarly, a reduction in the number of opportunities to learn will increase the uncertainty about whether one has accurately learned about the available behavioral options and their associated payoffs. We refer to the number of learning opportunities as an individual's effective lifespan to imply that it is the number of opportunities to learn throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.

Empirically, the number of learning opportunities can be manipulated in the lab, but will also correspond with an individual's age the real world. In multi-round studies of information use in novel tasks, US participants' use of social information declined precipitously across rounds ~\cite{McElreath2005}, suggesting they were more likely to use social information when they were most uncertain about the task early on. In a more naturalistic context, Aplin et al. (2017) \nocite{Aplin2017} found that younger great tits more readily used social information compared with older individuals, possibly because they had accrued less information via individual learning, and also possibly because younger individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options. 
% \ps{I got rid of the Leris and Reader reference because it didn't seem relevant to age-based uncertainty. They just showed that young guppies exposed to reliable models were more likely to use social information later. I also added some human studies, which seems important.} 
Cross-cultural studies on humans have shown the importance of childhood as a phase of heavy social learning ~\cite{Reyes2016}. Young children are more likely to acquire their beliefs and simple skills from their parents than are older children or adults, which is at least partly due to the differential knowledge accrual between young children and the older adults to whom they direct the most trust and attention \cite{kline2013teaching}.
%The age of individuals was found to have an effect on social learning in both \emph{parus major}~\cite{Aplin2017} and \emph{poecilia reticulata} (guppies)~\cite{Leris2016}. \ps{What effect? I'm not sure }
%\mt{Need better connection between lifespan and age, or better references to support use of lifespan}.
Individuals with shorter effective lifespans will end their lives with more uncertainty about which behaviors are optimal, and thereby transmit some of that uncertainty to anyone who learns from them. The effective lifespan for learning varies across tasks, individuals, and species, yet most models assume one learning opportunity per generation ~\cite{Feldman1996,Henrich1998, perreault2012bayesian}. Some models do allow several cultural generations within 1 genetic generation ~\cite{Enquist2007}, but little formal theory explicitly examines the role of uncertainty based on number of learning opportunities into our understanding of the evolution of social learning.

@@

% \begin{comment}

% \cm{I think a lot of this may be too much detail. I'm still editing and focusing the above on the main forms of uncertainty we are modeling and reviewing the relevant literature as we go. Yes we've made choices about things like horizontal vs vertical, but i think we can just justify that when we introduce the model }
% ps{I agree with Cristina here. I think we should use this section to justify our way of modeling individual and social learning, which is different from previous models. We don't need to provide a detailed review, just why it's worth doing it as we've done it. In particular, we should set up (1) social learning as an initial scaffold for future social learning, and (2) softmax individual learning which involves some greediness with occasional trial and error.}

% To add to confusion about how to integrate diverse models of social learning
% evolution, different models select different social learning components in
% seemingly \emph{ad hoc} ways 
% \begin{itemize}
%   \item 
%     Vertical, oblique, horizontal transmission
%   \item
%     Conformity, payoff-biased, frequency-dependent, etc. A note about how
%     ``conformity'' is often not distinguished from other forms of social learning
%   \item
%     Review human studies
%   \item
%     Review non-human studies~\cite{Leris2016,Aplin2017,Avargues-Weber2018,Baracchi2018}
%   \item
%     One sentence on how dual-inheritance theory enables us to gloss over whether
%     social learning is genetically or culturally evolved.
%   \item
%     More things from which we selected the operation of our model
% \end{itemize}

% \end{comment}

@@

In \emph{evolutionary} agent-based models like ours, agent life cycles are
programmed to cause agents to reproduce and die off, where reproducers pass on
heritable traits to their offspring. 
Natural selection occurs in the model when agents with higher
payoffs preferentially reproduce. This is a model of cultural evolution, so
``reproduction'' means teaching the meta-cognitive strategy of whether one should learn
socially at all; ``death'', in this interpretation, means
loss of the potential to socially influence others. 
This sets up an inter-generational structure
that we also use as a scaffold for social learning: we assume social learning occurs
\emph{obliquely}, meaning learning happens when a new
generation of agents each select a teacher from the previous generation, possibly
including their parents.  
Evolutionary agent-based models of cultural evolution are powerful, 
but their components need to be carefully specified and justified in relation to
empirical facts.

@@

@@

The model environment provides behaviors for agents to perform. The structure
of the environment is specified by setting several parameters, including
three of the uncertainty parameters: environmental variability, selection set size, 
and payoff ambiguity. 
Each behavior is indexed by $b$ and modeled as a ``one-armed bandit'', which yields 
Bernoulli-distributed payoffs of 1 with probability $\pi_b$ and 0 with 
probability $1 - \pi_b$. $\pi_b$ is equivalently the expected
payoff of behavior/bandit $b$. The model environment affords $B$ behaviors, where
$B$ is the \emph{selection set size} uncertainty parameter, which
is constant throughout the course of a given simulation.

The model environment is dynamic: which behavior is optimal changes between
generations with probability equal to the \emph{environmental variability}, $u$.
At the beginning of each generation, one bandit is optimal and yields expected
payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$. 
The \emph{payoff ambiguity} here between optimal and non-optimal behavior
payoffs is defined by $\pihigh - \pilow$. We set $\pihigh = 0.9$ to be constant
across all simulations, so our analysis only varies payoff ambiguity by varying
$\pilow$. Specifically, payoff ambiguity increases with $\pilow$. 
By systematically varying these uncertainty parameters we change
the nature of the challenge faced by the agents. Each parameter individually 
can increase or decrease ``uncertainty,'' but it is not at all clear \emph{a priori}
how these uncertainties combine to affect the evolution of social learning.
These uncertainty parameters and the values we tested in our simulations
are summarized in Table~\ref{tab:uncertaintyParameters}.

\vspace{2em}
\begin{table}[h]
\caption{Model ecological parameters, including uncertainty parameters $u$, $B$,
$\pilow$, and $L$. Bold indicates default value tested} %\emph{default value tested}.}
    \label{tab:uncertaintyParameters}
    \centering %\hspace{-3em}
    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule

@@

Agents are endowed with dynamic attributes to intelligently select behaviors and
calculate average payoffs for each behavior, and with a social learning trait value
that determines whether agents learn socially or not. All agents engage in
individual learning over their lifespan, whether or not they are social learners.
The difference between social learners and asocial learners is that social learners
have initially biased behavioral preferences based on information given to them by a
teacher of the previous generation. Asocial learners begin life with no behavioral
preferences. Agents and their learning procedures are specified through several
parameters introduced below.

\subsubsection{Individual learning}

All agents perform individual, trial-and-error learning at each time step in
their lifespan.  This learning is guided by softmax search which
drives agents to more frequently exploit the most profitable behaviors when the
agent is more certain which are optimal, and to explore more frequently when the
agent is unsure.  To do softmax searching, agents track average payoffs acquired
from each behavior, which also requires agents to track the number of times they
have performed each behavior.  We denote the average payoffs obtained by agent $i$
for behavior $b$ as $\ledger$. The number of times $i$ performed $b$ is $c_{ib}$
(``$c$'' stands for count).

At each time step, agents perform behavior $b$ 
with softmax-weighted probability
\begin{equation}
  \Pr(\text{Agent $i$ performs behavior $b$}) = 
    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}},
\end{equation}
\noindent
where $\beta$ is a parameter that adjusts how frequently agents perform 
behaviors with high expected payoffs (larger $\beta$) versus how frequently
agents explore alternative behaviors (smaller $\beta$)~\cite{McElreath2005}.

\subsubsection{Social learning}

At the beginning of each generation other than the first, social child agents select
one member of the previous generation to learn from if they are a social learner.
If agent $i$ is a social learner we write $s_i = 1$, and $s_i = 0$ otherwise.
A child agent $c$ is a social learner if its parent $p$ was a social learner,
i.e.\ $s_c \leftarrow s_p$, without mutation. 
Social learner children select a teacher from 
the previous generation by first selecting $N_T$ prospective teachers fully
at random, then by sampling from the $N_T$ with each prospective teacher weighted
by their net payoffs relative to the other $N_T - 1$.

\begin{table}[h]
  \vspace{2em}
  \caption{Agent-level variables. The first four ($\protect s_i$, $\protect
    \bar\pi_{ib}$, $\protect c_{ib}$,
  and $\protect \pi_i$) are dynamic with an implicit time dependence. The softmax
greediness $\protect \beta$ and number of prospective teachers for social learners,
$\protect N_T$, are constant throughout each simulation.}
    \label{tab:modelParameters}
    \centering %\hspace{-3em}
    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule

@@

Model dynamics proceed by first initializing the environment and agents according
to parameter settings for the simulation. Then, within each generation,
agents select and perform behaviors, updating their observations along the way.
Between generations, agents reproduce, teach child agents, and die off. 
Child agents then begin a new round of generational dynamics, followed by
reproduction. This process continues until the population has fixated as
all social learners or all asocial learners, or until an upper limit of 
iterations has been reached. This process is visualized in
Figure~\ref{fig:schematic}.

\paragraph{Initialization}

The model is initialized with $N$ agents, all with zero observed mean payoffs, 
$\ledger = 0$, and zero counts of how many times
they have tried each behavior, $c_{ib} = 0$ (Figure~\ref{fig:schematic}A).
At generation start, one of the behaviors is set to 
yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
expected payoffs $\pilow$. Agents are independently randomly initialized with $s_i
\in 0,1$.

\paragraph{Intragenerational dynamics}
% To guide behavior selection, agent $i$ counts how many times it
% performed each behavior $b$, denoted $c_{ib}$. Agents use this count to 
% update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
% $\ledger$ is initialized to 0 for all $b$ at model start for
% all agents (Figure~\ref{fig:schematic}A), and at 
% generation start for asocial learners. Social
% learning agents' $\ledger$ is initialized as that of its teacher, who is selected
% through performance-biased oblique learning; $c_ib$ is set to 1 for all social
% learners $i$ and behaviors $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
% accumulated payoffs from performing several behaviors over their lifetime of $L$
% time steps is denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write
% $s_i = 1$, otherwise the agent is an asocial learner and $s_i = 0$.

Within each generation, all $N$ agents perform $L$ behaviors sequentially and
independently (Figure~\ref{fig:schematic}B).
Agents make one choice for each step in its lifespan using softmax weighting
described above, updating the mean payoffs it has observed along the way. 
Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
bandit paid off. Behavior payoffs are drawn from a 
Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from
behavior $b$.  For concreteness we denote this probabilistic payoff
$\bandit$. After performing behavior $b$, agent $i$ updates the
corresponding \emph{behavior count} by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
the expected payoffs calculated for that behavior are updated with
exponentially-weighted averaging
\begin{equation}
  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}}.
\end{equation}
\noindent

\paragraph{Intergenerational dynamics}
In between generations agents first reproduce via asexual haploid reproduction; 
then new child agents learn from the
previous generation if they are social learners; and finally all agents from the
previous generation then die off (Figure~\ref{fig:schematic}C). 
$N$ reproducers are selected with replacement over $N$ independent draws, 
biased by performance:
\begin{equation}
  \Pr(\text{Agent $i$ is chosen to reproduce in one draw}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
\end{equation}
\noindent
A child inherits its parent's social learning trait $s_i$ without mutation.
A social learner child with $s_i = 1$ learns from a teacher from its parent's
generation, including possibly their parent (oblique learning). 
A child selects its teacher by first selecting $N_T$ prospective
teachers from the population completely at random, then selecting the one with
highest net payoffs $\pi_i$ as their teacher, with ties broken randomly. While it
is somewhat arbitrary to first subset $N_T$, this is a conservative choice that
represnts the fact that access to the entire population is not generally guaranteed.
Social learners adopt their chosen teacher's ledger of expected payoffs $\ledger$,
and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.  Asocial
learners ($s_i = 0$) are initialized with all $c_{ib} = 0$ and $\ledger = 0$ 
(Figure~\ref{fig:schematic}C). The
newly initialized population then begins behavior selection and payoff accumulation
for another $L$ time steps.

After reproduction and die-off, the optimal behavior changes with probability
$u$. If a random number draw indicates the behavior should change, the new
behavior is chosen from all behaviors but the current optimal behavior.

\paragraph{Stopping conditions} The evolutionary process continues until the
population reaches evolutionary fixation with repsect to social learning, where
$\sum_i s_i = 1$ or $\sum_i s_i = 0$, or until 20k iterations have run. 
It is rare for simulations not to reach fixation. We report how frequently
this happens in Table~\ref{tab:convergence}.

\subsection{Computational analyses}
\label{ssec:computationalAnalyses}

@@

To analyze the effect of the four principal uncertainty factors, we systematically
varied their values and observed three key outcome variables aggregated across 1000
trial simulations, and across all agents when appropriate. We varied $u \in \{0.0,
0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L
\in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.  We observed
three outcome measures: (1) $\meansl$, the average value of $s_i$ over all agents
and trials; (2) $\meanpi / L$, the average net payoffs at simulation end across
agents and trials, normalized by lifespan; and (3) $\meanT / L$, 
or the mean number of time steps to fixation normalized by
lifespan. We analyze outcomes by plotting $\meansl$ on the y-axis and environmental
variation is on x-axis since we theoretically expect that $\meansl$ will 
decrease monotonically from 1 to 0 as $u$ increases. We expected and observed
that the other three uncertainty factors shift the value of $u$ at which 
$\meansl$ starts to decrease, and how rapidly $\meansl$ decreases. Note that the
hypothesis-testing concept of significance is meaningless here because we could
make any small outcome difference ``significant'' by running more simulation trials.
We instead study the patterns of outcome 
variables over systematically varied uncertainty factor values.

@@

We performed sensitivity analyses to ensure that our main analysis is reasonably
robust to a range of auxiliary parameters. Specifically in our sensitivity analyses
we first varied the population size, $N$, to explore whether smaller $N$ would 
show more drift due to finite population size effects, but also generally support
our main conclusions. Next, we varied the
cognitive model parameter $\beta \in \{1, 100\}$ to supplement the main results
that used $\beta = 10$. Recall that $\beta$ sets how frequently the softmax algorithm
exploited the best observed behavior versus explored the rest. We do not
expect agents with different $\beta$ to perform equally well 
individually, so certain $\beta$ values may themselves suppress social learning
since individual learning itself may be unreliable. Nonetheless our results
should be valid over at least some range of $\beta$. Finally, we varied the
number of prospective teachers $N_T \in \{2, 10, 20\}$ 
to supplement the main results that used $N_T = 5$. The number of prospective
teachers should not change the whether social learning is optimal or not, 
but it may make model results driftier since the benefit of social learning should
be more difficult to detect with fewer prosopective teachers.

@@

To understand how different forms of uncertainty interact to affect the evolution
of social learning, we measured simulated social learning prevalence across a 
suite of simulations over uncertainty parameters. We analyze simulation outcomes
by plotting the mean observed social learning frequency, $\meansl$, across all agents 
and 1000 simulation trials for each uncertainty parameter setting. 
We visualize and inspect plots with $\meansl$ on the y-axis and
environmental variability, $u$ on the x-axis. This is convenient because we are
most certain about how $\meansl$ depends on $u$: we expect $\meansl$ to decrease
as $u$ increases since environmental variability is well understood to cause
socially-transmitted information to become outdated. When the other forms of
uncertainty are varied, this causes changes to when and how quickly social learning
is suppressed as $u$ increases. To inspect these changes, we show nine plots
of $\meansl$ over $u$ in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
Plot array columns correspond to different selection set sizes, $B$; rows
correspond to different non-optimal payoff values, $\pilow$ (recall optimal
payoff $\pihigh=0.9$ for all analyses); plot line and marker colors correspond
to different effective lifespan, $L$, values. 
We support our conclusions regarding the evolution of
social learning by analyzing the time to 
fixation and by comparing the average net payoffs in our simulations to the
expected payoffs for individuals in both populations of all social learners
and in populations of all individual learners. We thus use our analysis 
to understand changes to how $\meansl$ changes over $u$ for different uncertainty parameter settings.

Several patterns emerged in changes to social learning prevalence over
as the uncertainty parameters were varied (Figure~\ref{fig:mainResults}). 
First, we indeed observed that increased $u$ uniformly led to decreased
$\meansl$, across the other uncertainty parameter values. The other uncertainty
parameters changed at which value of $u$ that $\meansl$ started to decrease,
and how quickly $\meansl$ decreased. For example, 
when payoff ambiguity and selection set size were
both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when $u$ is small
since individual learning is relatively efficient in this case
(Figure~\ref{fig:mainResults}, upper left). As $\pilow$ increased,
$\meansl$ decreased less rapdily over $u$, which was more pronounced for smaller $L$ (rows of
Figure~\ref{fig:mainResults}).

Increased selection set size $B$ led nearly uniformly to more prevalent social
learning with all other uncertainty parameters being equal ($B$ increases along
columns in Figure~\ref{fig:mainResults}. 
This is because possibly misleading 
social information is less consequential due
to (1) larger $B$ is a more difficult problem for trial-and-error learning, and
(2) a misidentified optimal behavior is weighted less relative to smaller
$B$, meaning agents are more likely to explore behaviors identified as non-optimal
when $B$ is larger (columns of Figure~\ref{fig:mainResults}).  \mt{Support this by calculating the difference between weights when B=2 and B=10 and a social learner learns outdated information}
Increased $B$ led to more pronounced flattening of social learning suppression when
$L$ was small, apparently again because of the limited data available to evolution,
making individual outcomes more path dependent.

???$\pilow$ paragraph???
